Children’s Vocabulary Development in American Sign Language

### 2023-04-19 outputs/paper/paper.qmd
cross-referencing data visualizations

In this paper, we investigate the patterns and trends that occur during the early developmental years of childhood in terms of vocabulary in American Sign Language. The estimand that we are trying to estimate is the relationship between children's developmental ages and their production of vocabulary words in American Sign Language. We aimed to visualize the milestones for children's vocabulary development in sign language to compare it to the timeline of vocabulary development for speech-language. This paper uses data obtained from the open database, Wordbank, which exhibits information on the development of children's vocabulary in various languages. The dataset, "Full Child-by-Word", available on this database, provides information on the demographic details of each child when provided as well as the variables presenting their vocabulary assessment.

@@

```{r}
#| label: fig-fullchildbyword
#| fig-cap: Child's By American Sign Language (ASL) Word Overall Asseessment
#| echo: false
#| warning: false

@@

Discuss.

```{r}
#| echo: false

@@

Discuss.

```{r}
#| label: fig-childbywordprod
#| fig-cap: Child's Amount of Produced ASL Words
#| echo: false
#| warning: false

@@

Discuss.

@@

# READ MODEL INTO QUARTO DOCUMENT
prod_vocab_model <- readRDS(here::here("outputs/models/sim_prod_vocab_model.rds"))

@@

```{r}
#| label: fig-prodwordsmodel
#| fig-cap: Linear Model of Produced Words by Children Ages
#| echo: false
#| warning: false

@@

Discuss.

```{r}
#| echo: false

@@

>>>>

In this paper, we investigate the patterns and trends that occur during the early developmental years of childhood in terms of vocabulary in American Sign Language. The estimand that we are trying to estimate is the number of vocabulary words in American Sign Language that a child can produce at a given developmental age. We aimed to visualize the milestones for children's vocabulary development in sign language to compare it to the timeline of vocabulary development for speech-language. This paper uses data obtained from the open database, Wordbank, which exhibits information on the development of children's vocabulary in various languages. The dataset, "Full Child-by-Word", available on this database, provides information on the demographic details of each child when provided as well as the variables presenting their vocabulary assessment.

@@

```{r}
#| label: fig-fullchildbyword
#| fig-cap: Each child's overall assessment by American Sign Language (ASL) word, with their identification number arranged in ascending order of age.
#| echo: false
#| warning: false

@@

Discuss @fig-fullchildbyword.

```{r}
#| label: tbl-sumstats
#| tbl-cap: Summary statistics table of the children's ASL vocabulary assessment.
#| echo: false

@@

Discuss @tbl-sumstats.

```{r}
#| label: fig-childbywordprod
#| fig-cap: Each child's amount of produced ASL words, with their identification number arranged in ascending order of age.
#| echo: false
#| warning: false

@@

Discuss @fig-childbywordprod.

@@

# IMPORT MODEL FROM OUTPUTS FOLDER
prod_vocab_model <- readRDS(here::here("outputs/models/sim_prod_vocab_model.rds"))

@@

```{r}
#| label: fig-prodwordsmodel
#| fig-cap: Linear model of produced ASL words by children ages.
#| echo: false
#| warning: false

@@

Discuss @fig-prodwordsmodel.

```{r}
#| label: tbl-prodvocabmodelsum
#| tbl-cap: Model summary of produced words by children ages.
#| echo: false

@@

Discuss @tbl-prodvocabmodelsum.
